---
title: '8'
author: "Nikhil Gopal"
date: "11/12/2020"
output: pdf_document
---

**Question 1**

```{r}

data1 <- read.csv("/Users/nikhilgopal/Desktop/1.csv")

model <- lm(bp~rt, data = data1)

ttest <- t.test(data1$bp[data1$rt=="Placebo"], data1$bp[data1$rt=="Medication"])

summary(ttest)

```

There is a statistically significant difference in the 2 means, placebo group has a higher blood pressure than treatment group.

**Question 2**

```{r}
data2 <-read.csv("/Users/nikhilgopal/Desktop/2.csv")

data2$order_of_runs = as.factor(data2$order_of_runs)

modell <- lm(time~treatment_amount+order_of_runs, data = data2)

summary(modell)
```

It appears that this model fits the data very well, with an r^2 of 0.96. Treatment amount has a small effect on maze completion time, as an increase of 1 unit treatment will result in a 0.02 second increase in time. However, doses are increased by relatively small amounts that are nowhere close to 1 unit, so the effect of treatment is essentially negligible. The model shows that order of runs seems to be the most important variable that affects time. In the model, I made order of runs a factor so that R treated it as categorical instead of quantitative data.



**Question 3**

```{r}

data3 <- read.csv("/Users/nikhilgopal/Desktop/3.csv")

data3$amily = as.factor(data3$amily)
data3$subject = as.factor(data3$subject)

modelll <- lm(y~subject+amily+subject*amily, data = data3)

summary(modelll)
```

This model does not appear to fit the data well with an R^2 of 0.5. Also, some subjects and families affect the model more than others, meaning that there likely is not a relationship there.
