---
title: "Untitled"
author: "Nikhil Gopal"
date: "11/8/2020"
output: pdf_document
---
**Question 1**
```{r}

setwd("/Users/nikhilgopal/Google Drive/Notability/Applied Linear Regression Analysis/psets")

data <- read.csv("insurance.csv")

#Question 1

lin_mod <- lm(charges~age+sex+bmi+children+smoker+region, data = data)

lin_mod_log <-lm(log(charges)~age+sex+bmi+children+smoker+region, data = data)

hist(x=log(data$charges))

#log is the best transformation
```

**Question 2**

```{r}
#Age
mean(data$age)
sd(data$age)
min(data$age)
max(data$age)

#Sex
prop.table(table(data$sex))

#Smoker
prop.table(table(data$smoker))

#Children
mean(data$children)
sd(data$children)
min(data$children)
max(data$children)

#BMI
mean(data$bmi)
sd(data$bmi)
min(data$bmi)
max(data$bmi)

#Region
prop.table(table(data$region))

```

**Question 3**

```{r}

#Question 3
lm_age <- lm(charges~age, data = data)
summary(lm_age)
#f=131.2 on 1336 DF

lm_sex <- lm(charges~sex, data=data)
summary(lm_sex)
anova(lm_sex)

#p = 0.03615

lm_bmi <- lm(charges~bmi, data=data)
summary(lm_bmi)

#F = 54.71 on 1336 DF

lm_children <- lm(charges~children, data = data)
summary(lm_children)

#F = 6.206 on 1336 DF

lm_smoker <- lm(charges~smoker, data = data)
anova(lm_smoker)

#p is basically zero 2.2e^-16

lm_region <- lm(charges~region, data=data)
anova(lm_region)

#P = 0.03089

```


**Question 4**

```{r}
#Question 4
summary(lin_mod_log)
```

**Question 4.5**

```{r}
#Question 4.5
plot(x=data$charges,y=residuals(lin_mod_log), xlab = "Health insurance Charges (Dollars)", ylab = "Residuals of model using log on Y variable")

plot(residuals(lin_mod_log))
```

**Question 5**

I think the only insignificant factors in the model (in terms of effect) are sex and region. However, I would include them in the model, because they don't give a much higher R^2 when removed (meaning the model doesn't get much better without them), and because intutively it makes sense to me that having more variables in the model gives us a better prediction of effects on insurance charges. This model can also give us a better prediction for people that fall in those specific categories (sex/region), as opposed to people of both sexes or people in all regions.


**Question 6**

```{r}
poly1 <- lm(log(charges)~poly(age,3, raw = TRUE)+sex+data$smoker:bmi+children+data$smoker+region, data = data)
summary(poly1)
```

For this question, I was able to get the r^2 up to 0.78, up from 0.76. I added extra weight to age, and I multipled smoker status and BMI. I figured that old people likely had more health insurance charges, so I overweighted age in the model. I also figured that smokers who had high BMI's would have more charges, so I included that as an interaction. The increase in statistical significance was small, but the model I came up with was still better than the original model, and it makes sense intuitively.