---
title: "HW6"
author: "Nikhil Gopal"
date: "10/23/2020"
output: pdf_document
---

```{r}
setwd("C:/Users/d/Google Drive/Notability/Applied Linear Regression Analysis/psets/6")

data <- read.csv("week6.csv", header = FALSE)

names(data)[1] <- "Brain.Weight"
names(data)[2] <- "Body.Weight"
data[1,1] <- 3.385

```


**A**

```{r}
#A
linear_model <- lm(data$Brain.Weight ~ data$Body.Weight)

```

**B**

```{r}
#B
#variance is residual standard error^2
summary(linear_model)
```


Variance = 323.5

**C**

```{r}
linear_model
```

Slope = 0.90291
Intercept = -56.8555

**D**

```{r}
#D
summary(linear_model)
```

Standard error of slope: 0.04453
Standard error of intercept: 42.97805

**E**

Yi = (0.90291 * Xi) - 56.8555
Estimate = -55.04968

**F**

Standard error = 323.5


**G**

```{r}

#G
sterr <- 323.5

#pt function is t distribution
pvalue <- 2*pt(abs(sterr), df = 60, lower.tail = FALSE)

pvalue

```

The p value for this test was less than 0.001. Thus, we can safely say that the conditional expectation = 3.

**H**


```{r}
#H
#SSE = Residual Standard Error
#SST = sum((data$Brain.Weight - mean(data$Brain.Weight))^2)

SST = NULL

summary_model <- summary(linear_model)

SSE = summary_model$sigma^2 * 60
#SSR = SST - SSE
SSR = NULL

R2 <- summary_model$r.squared

MSE = SSE/(62-2)
MSR = SSR/1

SST
SSR
SSE
MSE
MSR


```

For the above question I commented out the SSR/SST lines, for some reason R was giving me an error with the formatting of the data, but I am confident that I have the correct method for generating those values with the commented out lines for this question. Would like to follow up in office hours.