---
title: "HW9"
author: "Nikhil Gopal"
date: "11/20/2020"
output: pdf_document
---

#Question 1

```{r}
#Question 1
library(ISLR)
data <- read.csv("psets/9/CaseControl_Listeriosis_Repos.csv")

sex <- glm(outcome~sex, data = data)
AC <- glm(outcome~AC, data = data)
SES <- glm(outcome~SES, data = data)
Residence <- glm(outcome~residence, data = data)
GAS <- glm(outcome~GAS, data = data)
IDT <- glm(outcome~IDT, data = data)
meat <- glm(outcome~meat, data = data)
packmeat <- glm(outcome~packmeat, data = data)

multiple_regression <- glm(outcome~sex+AC+SES+residence+GAS+IDT+meat+packmeat, data = data)

interactions <- glm(outcome~sex*GAS+sex+AC+SES+residence+GAS+IDT+meat+packmeat, data = data)
```

Our multiple regression analysis does not provide useful information on how to avoid developing the disease. The only variables that had a noticable affect on the outcome were GAS/IDT, and even these variables did not have much affect.


**Question 2**

```{r}
#Question 2

data2 <- read.csv("/Users/nikhilgopal/Google Drive/Notability/Applied Linear Regression Analysis/psets/9/2.csv")


risk_of_mortality <- glm(deaths~population+smoking.status+age, data = data2)
summary(risk_of_mortality)
```

It seems like age is one of the most impactful factors, more so than smoking status. Age is measured in groups of ten years, but the outcome variable increases by 50 for every ten years increase in age. Additonally, older people that smoke have an even higher risk of developing cancer, especially those that smoke often.